\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\title{CS311 Homework 1}
\author{Jason Dorweiler\\
	dorweilj@onid.oregonstate.edu\\
	CS211-400}
\begin{document}
\maketitle
\textbf{Question 2 Revision Control Systems }\\

Revision control systems are a way to manage and store past version of files.
They are useful because you can store previous version of a file and restore your current version if you were to mess something up.  It also allows others to work on a small portion of a large project and then merge their changes into the larger project.  \\

Git (Specifically commands for the GitHub version)

git push - update the remote repository

git fetch - download changes from remote repository

git clone - make a copy of a repository

git checkout - start work on a specific branch\\

RCS

mkdir RCS - initialize an RCS directory

rcsdiff - show what has changed in the file

co - checkout a file to work on

rcs -l - lock a file so no one else can check it out\\

SVN

create - create a new repository

checkout - start working on a local branch

list - show the current repositories in a list

status - show what files have changed\\

Mercurical (hg)

hg clone - make a local copy of a repository

hg diff - show changes in files

hg pull - update the local files

hg update - update the repository with changed files
\pagebreak

\textbf{Question 3 Piping vs. Redirection}

Redirection is a way to read from and write to files.  For example, you can redirect the output from $ls$ to some file using $>$.\\

Piping is a way to send data from one process to another.  Instead of saving data to a file you can sent it to another program.  An example that I always find helpful is piping the results from $ps$ to $grep$: $ps\ -A |\ grep\ firefox$ will give you the process id of firefox. \\

\textbf{Question 4 Find Command}
\begin{verbatim}
find . -type f -exec file '{}' \;
\end{verbatim}

\textbf{Question 5 Make}

Running make will start the GNU make program.  Make is most useful for finding which file in a large project needs to recompiled.  Large project can take a very long time to compile so only recompiling the update files saves a lot of time.\\
 
\end{document}